\section{Future Work}
\label{sec:future}

Our goal for this quarter was to create a few implementations in our language to
show that this concept is feasible and work further research. As such, we have a
plethora of future work that we would like to explore in the months to folow.
The first, which is seemingly intuitive, is that we want to implement more
functions in our language, so that it becomes a full fledged library, instead of
the test library as it stands now. Moreover, we need to create a syntax for our
language --- in it's current implementation, we have an AST, which can transform
into IR. Having a corresponding syntax is key to stabilize our language.

Currently, our language has only private labels --- we would like to expand it
to also utilize public labels. Along these lines, we also would like to expand
the notion of our side channel safety --- in it's current form, our language
prevents timing attacks. We would like to expand it to include memory safety and
prevention against memory side channels. This includes fixing our language so
that it does not index based on a secret value. 

Finally, a big future goal of this project is to determine a method of usability
testing for programming languages. A huge impediment in this task is that there
is no good way to test programming languages --- it is not a simple task that
you can assign humans, such as with mechanical turk \TK{reference}. One needs to
be able to find the key group of users, and be able to test it at a large scale
in order to get data about it. This is an open question that we are hoping to
address in the following months.
